Multi-channel Kondo model URG

### 2021-12-17 notes/mck_urg.tex
typo

\section{Role of the star graph in determining the physics of the problem}
Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the MCK models}. Instead, the RG flows converge to an intermediate coupling fixed point. The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}\textcolor{red}{, because the Hamiltonian commutes with the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\)~\cite{vondelft_prl_1998}}. For example, the two-channel and the three-channel Kondo models have ground state degeneracies of 2 and 3 respectively, throughout the RG flow. Analytic and numerical studies also showed that \textit{the two and three-channel models enjoy a weak-strong duality}~\cite{kroha_kolf_2007,zitko_fabrizio_2017}: the model at strong coupling, when projected onto the ground state basis, can also be thought of as a Kondo model at weak coupling, but possibly with a modified central spin. For example, in the two channel Kondo model, the model at strong coupling can be mapped onto the same model with a small coupling parameter, but with the central Kondo spin-half impurity replaced by a new, composite spin-half object formed by the doubly-degenerate ground state of the strong coupling model~\cite{kroha_kolf_2007}. The strong and weak coupling models are formally identical and the model is self-dual. The case of the three-channel model is different~\cite{zitko_fabrizio_2017} because there, the central impurity gets replaced by a new \textit{spin-1} impurity formed by the triply-degenerate ground state. Compared to the self-duality of the two-channel model, this case corresponds to a cross duality between a spin-\(\frac{1}{2}\) and a spin-1 model. We will now show that these qualitative features can be captured very simply by the star graph.

@@

\textcolor{red}{Just like the full Hamiltonian}, the star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel star graph. Since \(S^z\) commutes with the star graph, the ground states are eigenstates of \(S^z\) with distinct eigenvalues \(\frac{K+1}{2}, \frac{K-1}{2},\ldots,\frac{-K-1}{2}\). \textit{This feature - the equality of energy eigenvalue for distinct values of \(S^z\) - persists for all values of \(J \in \left[0^+, \infty^-\right]\)}. This is because, the gap between the degenerate subspace and the next excited level is \(J\) or \(\frac{J}{2}\), depending on whether \(K\) is even or odd, and the gap is always non-zero as long as \(J\) lies in the regime of RG flow. In other words, as the exchange coupling grows(shrinks) from \(0^+\left(\infty^-\right)\) towards the fixed point value \(J^*\), the degeneracy remains protected at \(K\). This is qualitatively different from the case of the single-channel Kondo model; there, the \(2-\)fold degeneracy of the local moment fixed point crosses over into a stable and unique singlet ground state at low temperatures/energies.

@@

\section{Strong-weak duality of the multi-channel Kondo RG flows}
We start from a strong coupling \((J \to \infty)\) spin-\(S\) impurity MCK Hamiltonian in the over-screened regime \(\left( K > 2S \right) \),
\begin{equation}\begin{aligned}
	\label{strong_ham}
	H(J) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J \vec{S_d}\cdot\vec{s}_\text{tot}~.
\end{aligned}\end{equation}
Here, \(\vec s_\text{tot}\) is the total spin \(\sum_l \sum_{kk^\prime \alpha\beta} \vec \sigma_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta,l}\) of all the zero modes. At strong-coupling, the ground states of the star graph eq.~\ref{zeromode_ham} act as a good starting point for a perturbative expansion. As argued previously, there are \(K-2S+1\) ground states, labelled by the \(K\) values of the total spin angular momentum \(S^z = S_d^z + s_\text{tot}^z = -\frac{K}{2} + S, -\frac{K}{2} + S + 1, \ldots, \frac{K}{2} - S\). To leverage the large coupling, one can define a new spin impurity \(\mathbb{S}\) out of this ground state manifold. Since the degeneracy of a spin is given by its multiplicity \(2S^\prime + 1\), we have \(2S^\prime + 1 = K-2S+1 \implies S^\prime = \frac{K}{2} - S\). That is, the spin-\(S\) impurity has a dual described by a spin-\((K-2S+1)\) impurity. The states of this new spin are defined by
\begin{equation}\begin{aligned}
	\mathbb{S}_d^z \ket{m_d^z} = m_d^z \ket{m_d^z}, &&\mathbb{S}_d^\pm \ket{m_d^z} \sim \ket{m_d^z \pm 1}
\end{aligned}\end{equation}
The excited states of the star graph can be used to define bosons \cite{kroha_kolf_2007}, and the hopping into the lattice can then be re-written using these bosons. One can then remove the single-particle hoping between the zero modes and the first sites using a Schrieffer-Wolff transformation in the small coupling \(J^\prime = \gamma \frac{4t^2}{J}\), and generate an exchange-coupling between the new impurity \(\vec {\mathbb{S}}_d\) and the new zero modes formed out of the remaining sites in the lattice \cite{kroha_kolf_2007} (by remaining, we mean those real space sites that have not been consumed into forming the new spin). The new Hamiltonian, characterised by the small superexchange  coupling \(J^\prime\), has the form
\begin{equation}\begin{aligned}
	H^\prime(J^\prime) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J^\prime \vec{\mathbb{S}_d}\cdot\vec{s^\prime}_\text{tot}
\end{aligned}\end{equation}
The prime on \(s_\text{tot}\) indicates that it is formed by the new zero modes. This Hamiltonian is very similar to the one in eq.~\ref{strong_ham}, and that is the essence of the strong-weak duality: One can go from the over-screened strong coupling spin-\(S\) MCK model to another over-screened weak coupling spin-\((K-2S+1)\) MCK model. For the case of \(K=4S\), we have \(S^\prime = S\), and both \(S_d\) and \(\mathbb{S}_d\) describe the same spin objects (at least formally). The two models are then said to be self-dual. For example, for the case of spin-half MCK model, two-channel model is self-dual.

>>>>

\section{Role of the star graph in determining the physics of the problem}
Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the MCK models}. Instead, the RG flows converge to an intermediate coupling fixed point. The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}\textcolor{red}. For example, the two-channel and the three-channel Kondo models have ground state degeneracies of 2 and 3 respectively, throughout the RG flow. Analytic and numerical studies also showed that \textit{the two and three-channel models enjoy a weak-strong duality}~\cite{kroha_kolf_2007,zitko_fabrizio_2017}: the model at strong coupling, when projected onto the ground state basis, can also be thought of as a Kondo model at weak coupling, but possibly with a modified central spin. For example, in the two channel Kondo model, the model at strong coupling can be mapped onto the same model with a small coupling parameter, but with the central Kondo spin-half impurity replaced by a new, composite spin-half object formed by the doubly-degenerate ground state of the strong coupling model~\cite{kroha_kolf_2007}. The strong and weak coupling models are formally identical and the model is self-dual. The case of the three-channel model is different~\cite{zitko_fabrizio_2017} because there, the central impurity gets replaced by a new \textit{spin-1} impurity formed by the triply-degenerate ground state. Compared to the self-duality of the two-channel model, this case corresponds to a cross duality between a spin-\(\frac{1}{2}\) and a spin-1 model. We will now show that these qualitative features can be captured very simply by the star graph.

@@

The star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel spin-half star graph. Since \(S^z\) commutes with the star graph, the ground states are eigenstates of \(S^z\) with distinct eigenvalues \(\frac{K+1}{2}, \frac{K-1}{2},\ldots,\frac{-K-1}{2}\). \textit{This feature - the equality of energy eigenvalue for distinct values of \(S^z\) - persists for all values of \(J \in \left[0^+, \infty^-\right]\)}. This is because, the gap between the degenerate subspace and the next excited level is \(J\) or \(\frac{J}{2}\), depending on whether \(K\) is even or odd, and the gap is always non-zero as long as \(J\) lies in the regime of RG flow. In other words, as the exchange coupling grows(shrinks) from \(0^+\left(\infty^-\right)\) towards the fixed point value \(J^*\), the degeneracy remains protected at \(K\). This is qualitatively different from the case of the single-channel Kondo model; there, the \(2-\)fold degeneracy of the local moment fixed point crosses over into a stable and unique singlet ground state at low temperatures/energies.

@@

\section{Strong-weak duality of the multi-channel Kondo RG flows}
We start from a strong coupling \((J \to \infty)\) spin-\(S\) impurity MCK Hamiltonian in the over-screened regime \(\left( K > 2S \right) \),
\begin{equation}\begin{aligned}
	\label{strong_ham}
	H(J) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J \vec{S_d}\cdot\vec{s}_\text{tot}~.
\end{aligned}\end{equation}
Here, \(\vec s_\text{tot}\) is the total spin \(\sum_l \sum_{kk^\prime \alpha\beta} \vec \sigma_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta,l}\) of all the zero modes. At strong-coupling, the ground states of the star graph eq.~\ref{zeromode_ham} act as a good starting point for a perturbative expansion. As argued previously, there are \(K-2S+1\) ground states, labelled by the \(K\) values of the total spin angular momentum \(S^z = S_d^z + s_\text{tot}^z = -\frac{K}{2} + S, -\frac{K}{2} + S + 1, \ldots, \frac{K}{2} - S\). To leverage the large coupling, one can define a new spin impurity \(\mathbb{S}\) out of this ground state manifold. Since the degeneracy of a spin is given by its multiplicity \(2S^\prime + 1\), we have \(2S^\prime + 1 = K-2S+1 \implies S^\prime = \frac{K}{2} - S\). That is, the spin-\(S\) impurity has a dual described by a spin-\((K-2S+1)\) impurity. The states of this new spin are defined by
\begin{equation}\begin{aligned}
	\mathbb{S}_d^z \ket{S^z} = S^z \ket{S^z}, &&\mathbb{S}_d^\pm \ket{S^z} = \sqrt{S^\prime\left( S^\prime + 1 \right) - S^z\left( S^z \pm 1\right)} \ket{S^z \pm 1}
\end{aligned}\end{equation}
The excited states of the star graph can be used to define bosons \cite{kroha_kolf_2007}, and the hopping into the lattice can then be re-written using these bosons. One can then remove the single-particle hoping between the zero modes and the first sites using a Schrieffer-Wolff transformation in the small coupling \(J^\prime = \gamma \frac{4t^2}{J}\), and generate an exchange-coupling between the new impurity \(\vec {\mathbb{S}}_d\) and the new zero modes formed out of the remaining sites in the lattice \cite{kroha_kolf_2007} (by remaining, we mean those real space sites that have not been consumed into forming the new spin). The new Hamiltonian, characterised by the small superexchange  coupling \(J^\prime\), has the form
\begin{equation}\begin{aligned}
	H^\prime(J^\prime) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J^\prime \vec{\mathbb{S}_d}\cdot\vec{s^\prime}_\text{tot}
\end{aligned}\end{equation}
The prime on \(s_\text{tot}\) indicates that it is formed by the new zero modes. This Hamiltonian is very similar to the one in eq.~\ref{strong_ham}, and that is the essence of the strong-weak duality: One can go from the over-screened strong coupling spin-\(S\) MCK model to another over-screened weak coupling spin-\((K-2S+1)\) MCK model. For the case of \(K=4S\), we have \(S^\prime = S\), and both \(S_d\) and \(\mathbb{S}_d\) describe the same spin objects (at least formally). The two models are then said to be self-dual. For example, for the case of spin-half MCK model, two-channel model is self-dual.
